### 2018-05-09 Paper/method.tex
updated alg 1 ...

\begin{breakablealgorithm}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
    \Procedure{Screening}{}
      \State Generate $n_1$ samples in $\mathbb{R}^{N_p}$ according to the joint probability density, $\bm{f(\theta)}$.
      \State Evaluate the gradient vector, $\nabla_{\bm{\theta}}G_k$ at each sample point, $\bm{\theta}_k$.
      \State Approximate sensitivity measures, $\bm{\mu}$: \be\bm{\mu} \approx \hat{\bm{\mu}} = 
      \frac{1}{n_1}\sum\limits_{k=1}^{n_1}(\nabla_{\bm{\theta}}G_k)(\nabla_{\bm{\theta}}G_k)^{T}\nonumber\ee
      \State Estimate $\widehat{\mathcal{C}_i\mu_i}$ for each parameter, $\theta_i$ and determine initial ranks,
       $\mathcal{R}^{old}$.
      \State set $s$ = 1\Comment{Iteration counter}
      \Do
        \State Generate $n_s$ new points in $\mathbb{R}^{N_p}$.
        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
        \State Compute $\Delta\mu_m$ = max$\left(\frac{|\mu_{i,s} - 
               \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.\Comment{$\Delta\mu_m$:
               Maximum deviation in $\mu_i$ between successive iterations.}
        \State set $s$ = $s$ + 1
      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
               $\Delta\mu_m$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
    \EndProcedure
  \end{algorithmic}
\end{breakablealgorithm}

>>>>

\clearpage
\begin{breakablealgorithm}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
    \Procedure{Screening}{}
      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
       according to the probability density $\bm{f(\theta)}$.
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k = 1, \ldots, n_1$.

      \State Compute 
      $\mu_{1, i} = \frac{1}{n_1} \sum_{k = 1}^{n_1} (g^k_i)^2$
      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
             $i = 1, \ldots, \Np$. 
      \State Determine initial ranks: 
            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{n_1}$ such that 
\[
   \nu_{\sigma(1)} \geq \nu_{\sigma(2)} \geq \cdot \geq \nu_{\sigma(\Np)}. 
\]
      \State Set $s$ = 1.
      \State Set $\mathrm{done} = \mathrm{false}$.
      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
        \State Set $s = s + 1$.
        \State Draw $n_s$ new samples 
                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.

        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
               $\{\bm{g}_k \}_{k = 1}^{n_{s-1}+n_s}$.
        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
               \left(\frac{|\mu_{i,s} - \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.
      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
         \State $\mathrm{done} = \mathrm{true}$
      \Else
          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
      \EndIf
    \EndWhile
    \EndProcedure
  \end{algorithmic}
\end{breakablealgorithm}
